Differentiable Optics with {\Large $\partial$}Lux: I - Deep Calibration of Flat Field and Phase Retrieval with Automatic Differentiation

### 2023-04-14 src/tex/ms.tex
[showyourwork] overleaf sync

This optimisation strategy performs well, with Figure~\ref{fig:data_residual} showing the final residual image with no visually discernable structure. A further analysis of parameter recovery over a range of fluxes and PRFs is shown in Section~\ref{sec:noise}. Correlations and residual plots of the positions, fluxes and aberrations after the optimisation are shown in Figure~\ref{fig:astro_params} and Figure~\ref{fig:aberrations}. Figure~\ref{fig:aberrations} shows the recovery of the optical aberrations, with a final residual aberration of 
% \textcolor{red}{showyourwork variable}
% \variable{output/rms_opd_resid.txt} 
0.0499\,nm RMS. \textcolor{red}{update with final values}
Finally, Figure~\ref{fig:flat_field} shows a correlation plot of the true and recovered sensitivity values and the corresponding residual histogram. The points of the correlation plot are colour-coded with the total counts for each pixel, showing as expected that pixels with higher photon counts having a better recovery of the \ac{prf} since these pixels have a greater \ac{snr}. Overall the parameters are very well recovered down to the noise level.

>>>>

This optimisation strategy performs well, with Figure~\ref{fig:data_residual} showing the final residual image with no visually discernable structure. A further analysis of parameter recovery over a range of fluxes and PRFs is shown in Section~\ref{sec:noise}. Correlations and residual plots of the positions, fluxes and aberrations after the optimisation are shown in Figure~\ref{fig:astro_params} and Figure~\ref{fig:aberrations}. Figure~\ref{fig:aberrations} shows the recovery of the optical aberrations, with a final residual aberration of 0.0282\,nm RMS.

Finally, Figure~\ref{fig:flat_field} shows a correlation plot of the true and recovered sensitivity values and the corresponding residual histogram. The points of the correlation plot are colour-coded with the total counts for each pixel, showing as expected that pixels with higher photon counts having a better recovery of the \ac{prf} since these pixels have a greater \ac{snr}. Overall the parameters are very well recovered down to the noise level.
